Concurrent Programming in Harmony

### 2020-10-09 book/paper.tex
Fixed bug in pointer checking

Harmony does not complain about \autoref{fig:rwbusy}, but, using
the right test, Harmony can be used to check for busy-waiting.
\autoref{fig:rwblock} presents such a test.
Note that the initialization code obtains a read lock, preventing
all readers and writers from entering the critical section.
In that case, those processes should ideally be blocked and Harmony
can test for that by running it with the \texttt{-b} flag.
This flag tells Harmony to check
that all states are non-terminating and lead to a state in which
all processes are blocked.

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Anneke van Renesse,
Brendon Nguyen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.

>>>>

Harmony does not complain about \autoref{fig:rwbusy}, but, using
the right test, Harmony can be used to check for busy-waiting.
\autoref{fig:rwblock} presents such a test.
Note that the initialization code obtains a write lock, preventing
all readers and writers from entering the critical section.
In that case, those processes should ideally be blocked and Harmony
can test for that by running it with the \texttt{-b} flag.
This flag tells Harmony to check
that all states are non-terminating and lead to a state in which
all processes are blocked.

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Anneke van Renesse,
Brendon Nguyen,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.
